Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-07-29 SDSS Journal Paper/Paper Draft.Rmd
Fix bib formatting - consistency

Using the framework from "Creating design guidelines for building city dashboards from a user's perspectives" [@young], we will help summarize a users concerns utilizing six main critiques, which are framed into questions. We will adapt these questions to better help the town leaders communicate clear feedback for our team to use. We will collect how the users are experiencing the app with these set questions:
\begin{itemize}
\item Is the information the dashboard presents clear? \textit{(Scope)}
\item Is the dashboard easy to navigate? \textit{(Usability)}
\item Is the dashboard used in a socially responsible manner? \textit{(Ethics)}
\item Do you believe that you can trust the Rural Shrink Smart dashboard? \textit{(Validity)}
\item Do you find value in the Rural Shrink Smart dashboard? \textit{(Utility)}
\end{itemize}

>>>>

Using the framework from "Creating design guidelines for building city dashboards from a user's perspectives" [@lee], we will help summarize a users concerns utilizing six main critiques, which are framed into questions. We will adapt these questions to better help the town leaders communicate clear feedback for our team to use. We will collect how the users are experiencing the app with these set questions:
\begin{itemize}
\item Is the information the dashboard presents clear? \textit{(Scope)}
\item Is the dashboard easy to navigate? \textit{(Usability)}
\item Is the dashboard used in a socially responsible manner? \textit{(Ethics)}
\item Do you believe that you can trust the Rural Shrink Smart dashboard? \textit{(Validity)}
\item Do you find value in the Rural Shrink Smart dashboard? \textit{(Utility)}
\end{itemize}
